Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-06 paper/paper.Rmd
contribued to case study section

To show the effect of spatial autocorrelation on performance estimates in cross-validation, a spatial and non-spatial CV using method `"spatial_coords"` will be shown in the following.

The performance of a simple classification tree (`"classif.ranger"`) is evaluated on a repeated cross-validation (`"repeated_cv"`) with four folds and two repetitions.
In reality, more fold (between five and ten) and a higher number of repetitions should be used.
The chosen evaluation measure is the "Area Under the ROC Curve" (`"classif.auc"`) which is a common evaluation measure for binary responses.
The CV will be executed twice with the only difference being the use of a spatial resampling object (initialized with `rsmp("repeated_spcv_coords"`) instead of a non-spatial one (`rsmp("repeated_cv"`).

>>>>

To show the effect of spatial autocorrelation on performance estimates in cross-validation, we will apply spatial and non-spatial cross-validation to the prediction of landslides using the random forest technique (`"classif.ranger"`).
Specifically, we use spatial partitioning based on $k$-means clustering of the coordinates (method `rsmp("repeated_spcv_coords")`) and compare its results to a non-spatial (random) cross-validation (`rsmp("repeated_cv")`), both with (only) four folds and two repetitions for demonstration.
We choose the area Under the ROC curve (`"classif.auc"`) as the performance measure for this 'soft' classification task.
